### 2017-11-18 Risk analysis/Text/Layout/Layout/chapter4_discussion.tex
In discussion

	Based on the recent findings by \citet{delaVarga2016}, showing that structural modeling can be viewed as a problem of Bayesian inference, the aim of this work was to extend this approach by considering practical applications and the utility geological modeling might have in an economic context. A sector in which structural geological modeling is of central importance and commonly used is hydrocarbon exploration. This field is characterized by the necessity to regularly make decisions in the face of high risks and potentially high rewards. As these decisions are often closely linked to geological modeling and the estimation of reservoir-related values, this work aimed to use this context to extend the Bayesian inference step in geological modeling by evaluating its results in terms of influence on decision making. It was initially hypothesized that Bayesian updating by using likelihoods and the resulting change in uncertainty in a model, should have significant effects on subsequent decision-making.\\
	To observe this, geological models were interpreted as potential hydrocarbon systems. Algorithms for structural trap recognition and calculation of values relevant to respective decision-making were developed. A custom loss function was designed to express the environment in which such values are to be estimated and to represent preferences of differently risk-affine decision makers. These methods were for a conceptual 1D geological model and subsequently for a 3D structural model. Despite the great leap in complexity, the results from both models are widely similar. According to these, conducting Bayesian inference in the context of structual geological modeling of hydrocarbon system induced several main effects on reservoir value probability distributions and the consequent estimation step, i.e. the decision-making.\\
	Changes in the posterior score and $ROV$ distributions were characterized by shifting of probabilities, as well as raising and narrowing of modes. The latter effect can be interpreted as a translation of uncertainty reduction in the model, to uncertainty reduction in the resulting distribution. Lateral shifting can be related to modes of the distribution as well as the distribution as a whole. ...\\
	One major observation to be named is that it seem to be of central importance "where" in the model uncertainty is reduced, i.e. in which spatial area or regarding which model parameter. This appears to be of particular importance considering threshold values that lead to an abrupt cut-off and duality in the decision-making. In both types of model construction, 1D and 3D, this was directly related to sealing reliability. Thresholds regarding seal thickness (1D model) and Shale Smear Factor ($SSF_c$ in 3D model) had been defined in a way that introduced a significant possibility of complete failure of a trap. Consequently, it was observed that reducing the uncertainty in a way that narrowed the probability of a threshold-related parameter around its cut-off value, led to an amplification of large-scale bimodality of the score or $ROV$ probability distribution. Resulting Bayes action were characterized by an increased divergence, i.e. disagreement between the estimates of different decision-makers. Thus, it appears suitable to introduce a differentiation between model uncertainty and decision uncertainty. Reducing model uncertainty in the "wrong" areas seems to simply lead to a transformation of this uncertainty in the realm of decision-making. Overall uncertainty seems to be conserved, as the duality of the decision problem is amplified in the form of a more stretched-out bimodal distribution and diverging Bayes actions. According to this, it should be a foremost importance for each actor, to reduce the uncertainty regarding threshold-related factors which might decide between "success" and complete failure of a project.\\
	It furthermore can be argued that the degree of convergence of Bayes actions is a measure for the state of knowledge during the decision-making process.

	3: high risk related to seal-reliability --> main factor for decision making: important to look for right "area" to reduce uncertainty

@@

	1D CASE:

				-abstract case: easy model construction and straightforward design of a loss function making basic assumptions and taking relative values that can simply be exchanged

				-so representative in a "relative" way, mostly appropriate to illustrate principles and benefits of the methodology

				-decision making/ estimation is defined by the design of the loss function which includes framework parameters which depend on the problem environment (e.g. market, technical constraints, etc.)

				-similar actors but different behaviors concerning risk: different decisions but same general loss function path (just different minima of EL)

				-additional information changes decision (BA) and EL

				-magnitude of change varies not only with the nature of the information (magnitude of uncertainty reduction) but also with the risk parameter

				-some actors might benefit more from some specific additional information than others

				-quantifiable value of information??

				- The GREATER the REDUCTION IN UNCERTAINTY, the LOWER the relevance of the risk-factor and difference in actor's preferences

				- accurate decision-making vs. gaining of information that yields encouraging results (vs "disappointing" results)

	WHERE in the MODEL uncertainty is reduced is SIGNIFICANT for the DECISION MAKING PERSPECTIVE:
	uncertainty might be reduced greatly in a model, e.g. looking at IE,
	but this might happen to lead to high probabilities at areas which are critical to the decision-making problem, such as areas at which a threshold has been defined, leading to a stark cut-off limit between YES and NO (two extrema of decisions)
	==> so maybe, while the objective model-related uncertainty has been reduced, the DECISION UNCERTAINTY remains constant or might even rise??

>>>>

	Building upon the recent findings by \citet{delaVarga2016}, showing that structural modeling can be viewed as a problem of Bayesian inference, the aim of this work was to extend this approach by considering practical applications and the utility geological modeling might have in an economic context. A sector in which structural geological modeling is of central importance and commonly used is hydrocarbon exploration. This field is characterized by the necessity to make decisions in the face of high risks and potentially high rewards. As these decisions are often closely linked to geological modeling and the estimation of reservoir-related values, this is work aimed to use this context to extend the Bayesian inference step in geological modeling by evaluating its results in terms of influence on decision-making. It was initially hypothesized that Bayesian updating by using likelihoods and the resulting change of uncertainty in a model, should have significant effects on subsequent decision-making.\\
	To analyze this, geological models were interpreted as potential hydrocarbon systems. Algorithms for structural trap recognition and calculation of values relevant to respective decision-making were developed. A custom loss function was designed to express the environment in which such values are to be estimated and to represent preferences of differently risk-affine decision-makers. These methods were applied for a conceptual 1D geological model and subsequently for a 3D structural model. Despite the great leap in complexity, the results from both models are widely similar. According to these, conducting Bayesian inference in the context of structural geological modeling of hydrocarbon system induces several main effects on reservoir value probability distributions and the consequent estimation step, i.e. the decision-making.\\
	As score and $ROV$ probability distributions were defined to depend on model parameters directly, but also on their values related to other parameters and specific thresholds, changing the model uncertainty naturally resulted in a change of shape of related posterior distributions. For both model designs, the prior value probability distributions were characterized by a distinct bimodality formed by widely separated modes of opposing values (positive vs. negative or zero). By introducing likelihood functions, these modes were most often shifted or altered in their shape. The latter was observed as either an amplification of the mode, by raising its mean probability, while narrowing the range of probabilities (i.e. reducing the standard deviation), or the opposite, a diminishment of the mode up to total erasure of its probability. These changes were often accompanied by lateral shifting of a mode. It can be argued that these processes reflect a translation of the model uncertainty into uncertainty in the reservoir value distribution. Within this it can be differentiated between uncertainty related to single modes, and uncertainty regarding the overall distribution. In some inference cases, the degree of bimodality was increased. This was caused by amplificaton of one of the modes, while the other remained constant or was also raised. So while uncertainty was reduced for one or both modes, the overall spread of probabilities and thus the total uncertainty was conserved, indicated by the mean of the whole distribution located in between both modes. In other cases, one mode was diminished or even completely erased, while the other was amplified. Resulting in overall unimodal distributions with centralized means, characterized accordingly by a reduction in total uncertainty. As the process of decision-making is based on these value distributions by applying the custom loss function respectively, this overall uncertainty might well be referred to as "decision uncertainty", here.\\
	The decision-making of differently risk-affine actors, i.e. the position and spread of Bayes actions, changed relative to the properties of value probability distributions and their inherent decision uncertainty. Distinct bimodality between two extremes, i.e. high decision uncertainty, resulted in a higher spread of Bayes estimators. Reduction of the distribution to one mode conversely led to the convergence of different Bayes actions. Reduction of the overall decision uncertainty furthermore was accompanied by a decrease in expected loss for each decision. Consequently, it can be argued that the degree of convergence of Bayes actions and their expected loss can be considered measures for the state of knowledge during the decision-making process. The better this is, the more similar the decisions of differently risk-affine actors are. It can be assumed that given perfect information, all actors would bid on the same estimate, the true value, and expect no loss. The relevance of the risk-factor consequently decreases with higher reduction of decision uncertainty.\\
	One major observation to be named is that it seem to be of central importance "where" in the model uncertainty is reduced, i.e. in which spatial area or regarding which model parameter. This appears to be of particular significance considering threshold values that lead to an abrupt cut-off between two extrema of decision options. In both types of model construction, 1D and 3D, this is directly related to sealing reliability. Thresholds regarding seal thickness (1D model) and Shale Smear Factor ($SSF_c$ in 3D model) were defined in a way that introduced a significant possibility of complete failure of a trap. Consequently, it was observed that reducing the uncertainty in a way that narrowed the probability of a threshold-related parameter around its cut-off value, led to an amplification of the respective mode (negative or zero values) and thus emphasized the risk of complete failure. Resulting Bayes actions were characterized by an increase in divergence and expected losses. Reducing model uncertainty in the "wrong" areas seems to simply lead to a transformation of this uncertainty in the realm of decision-making. Overall uncertainty seems to be conserved or even increased (see 3D posterior model V), as the duality of the decision problem is amplified in the form of a more stretched-out bimodal distribution and diverging Bayes actions. According to this, it should be of foremost importance for each actor, to reduce the uncertainty regarding threshold-related factors which might decide between "success" and complete failure of a project. Some type of information might improve the potential for a positive outcome, but maintain the risk of failure. For making better decisions, elimination of such high risks should be a priority. In the context of hydrocarbon traps, this is greatly influenced by seal reliability.\\

	- IE not adequate method for finding this "where", as such a threshold value might dependent on more on the relation of different parameters, than on the realization of one in the model

	It has too be emphasized that the models constructed in this work were purely artificial and not based on real data. However, the 3D model in particular was designed to include some typical structural characteristics related to hydrocarbon systems and algorithms were developed to consider the most common conditions that define structural traps. The fact that similar observations were made for the 1D, as well as the 3D model, indicates that these might be appropriately representative to conceptually visualize the effects of the methods.\\
	For the purpose of a conceptual application, the customization of the loss functions was kept relatively simple. In fact, as it incorporated only a few basic assumptions, it might thus be more generally representative than a complex function which takes into account too specific aspects. The consideration of more details would have furthermore required extensive speculation, which would have presumably impaired the generalization potential of respective observations.

@@
